Non-intrusive reduced order modeling of nonlinear problems \\ using neural networks

### 2018-01-25 revision/RBMNN_response_to_reviewers.tex

			\item \emph{In terms of future work, do you foresee such methods becoming applicable beyond steady-state problems (i.e. problems with intermittent dynamics)? What are the main limitations there?} \\[0.3cm]
			As said in the Conclusion (page $25$, line $704$), the extension of the proposed method to time-dependent parameterized problems should be investigated in the future. In this respect, let us remark that the generation of the reduced space is totally decoupled from the training and evaluation of the neural networks (page $26$, Conclusion, lines $706-707$). For instance, in the case of Hamiltonian systems, a reduced basis could be extracted via the structure-preserving greedy approach proposed by Afkham \& Hesthaven \cite{AH17}. Further, ROMs built via the POD-NN algoruthm seem to have better stability properties, as compared to traditional projection-based ROMs. This speculation is based on the results regarding the lid-driven cavity problem, where the POD-NN ROM turns out not to require any stabilizing technique. Hence, we believe that our method could be applied to a broad class of PDE problems.
		\end{enumerate}

	\section*{References}
	\begin{thebibliography}{50}
		\bibitem{AH17}
		Afkham, B. M., Hesthaven, J. S. (2017). \emph{Structure preserving model reduction of dissipative Hamiltonian systems}. Submitted to Journal of Scientific Computing.

		\bibitem{GMW81}
		Gill, P. E., Murray, W., Wright, M. H. (1981). \emph{Practical optimization}. Academic Press.

		\bibitem{Hag94}
		Hagan, M. T., Menhaj, M. B. (1994). \emph{Training feedforward networks with the Marquardt algorithm}. IEEE Transactions on Neural Networks, 5(6):989-993.

		\bibitem{Hag96}
		Hagan, M. T., Demuth, H. B., Beale, M. H. (1996). \emph{Neural Network Design}. Boston, MA: PWS Publishing.

		\bibitem{Kri07}
		Kriesel, D. (2007). \emph{A Brief Introduction to Neural Networks}. Retrieved from \url{http://www.dkriesel.com/en/science/neural_networks}.

		\bibitem{Mar63}
		Marquardt, D. W. (1963). \emph{An algorithm for least-squares estimation of nonlinear parameters}. Journal of the Society for Industrial and Applied Mathematics, 11(2):431-441.

		\bibitem{Mol93}
		M\o{}ller, M. D. (1993). \emph{A scaled conjugate gradient algorithm for fast supervised learning}. Neural Networks, 6:525-533.
	\end{thebibliography}
\end{document}
